Dynamical modeling of tidal streams

### 2013-12-30 tex/ms.tex
streams: cut-out version of l figures

\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lb.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_ld.ps}
  \caption{Simulated stream after $5.011\Gyr$ as a function of Galactic
    longitude. The top panel shows the stream in Galactic latitude and
    the bottom panel shows the distance from the Sun. The progenitor
    is shown as the large gray dot and its orbit as the dashed
    lines. The predicted track of the stream is shown as the solid
    line. Insets show various zoomed-in parts of the stream to show
    the stream, progenitor orbit, and predicted stream track up
    close.}\label{fig:gd1_lbd}
%python plot_stream.py ../tex/gd1_evol_lb.ps
%python plot_stream.py ../tex/gd1_evol_ld.ps
\end{figure}

\begin{figure}[tp!!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lvlos.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lpmll.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lpmbb.ps}
  \caption{Simulated stream velocities as a function of Galactic
    longitude. Same as \figurename~\ref{fig:gd1_lbd}, but for the
    stream in heliocentric line-of-sight velocity $V_{\mathrm{los}}$
    (top panel), proper motion in the direction of Galactic longitude
    (middle panel), and in the direction of Galactic latitude (bottom
    panel). Insets again show various interesting parts of the stream
    up close.}\label{fig:gd1_lbv}
%python plot_stream.py ../tex/gd1_evol_lvlos.ps
%python plot_stream.py ../tex/gd1_evol_lpmll.ps
%python plot_stream.py ../tex/gd1_evol_lpmbb.ps
\end{figure}

>>>>

\begin{figure}[t!]
  \includegraphics[width=0.8\textwidth,clip=]{gd1_evol_lb.eps}
  \includegraphics[width=0.8\textwidth,clip=]{gd1_evol_ld.eps}
  \caption{Simulated stream after $5.011\Gyr$ as a function of Galactic
    longitude. The top panel shows the stream in Galactic latitude and
    the bottom panel shows the distance from the Sun. The progenitor
    is shown as the large gray dot and its orbit as the dashed
    lines. The predicted track of the stream is shown as the solid
    line. Insets show various zoomed-in parts of the stream to show
    the stream, progenitor orbit, and predicted stream track up
    close.}\label{fig:gd1_lbd}
%python plot_stream.py ../tex/gd1_evol_lb.ps
%python plot_stream.py ../tex/gd1_evol_ld.ps
\end{figure}

\begin{figure}[tp!!]
  \includegraphics[width=0.8\textwidth,clip=]{gd1_evol_lvlos.eps}
  \includegraphics[width=0.8\textwidth,clip=]{gd1_evol_lpmll.eps}
  \includegraphics[width=0.8\textwidth,clip=]{gd1_evol_lpmbb.eps}
  \caption{Simulated stream velocities as a function of Galactic
    longitude. Same as \figurename~\ref{fig:gd1_lbd}, but for the
    stream in heliocentric line-of-sight velocity $V_{\mathrm{los}}$
    (top panel), proper motion in the direction of Galactic longitude
    (middle panel), and in the direction of Galactic latitude (bottom
    panel). Insets again show various interesting parts of the stream
    up close.}\label{fig:gd1_lbv}
%python plot_stream.py ../tex/gd1_evol_lvlos.ps
%python plot_stream.py ../tex/gd1_evol_lpmll.ps
%python plot_stream.py ../tex/gd1_evol_lpmbb.ps
\end{figure}
